---
title: "developing data products week 4 final project"
author: "Peter"
date: "January 30, 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Coursera Reproducible Pitch


### See the Regression Models Course Project  


- URL: *https://github.com/PeterAF93/developing-data-products-week-4-assignment*
- Find here all the data that have been use for this presentation and also for the first part of the data Science Project: "First, you will create a Shiny application and deploy it on Rstudio's servers.Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application."


### Find all details here
URL: *https://www.coursera.org/learn/data-products/peer/tMYrn/course-project-shiny-application-and-reproducible-pitch*


---



## mtcars Dataset


### Motor Trend Car Road Tests

```{r}
?mtcars

```

> The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

```{r}
library(datasets)
head(mtcars)
```

---


## mtcars Dataset - Format


**A data frame with 32 observations on 11 variables.**


| Index | Field | Detail |
------- | ----- | ------ |
| [, 1] | mpg | Miles/(US) gallon |
| [, 2]  | cyl | Number of cylinders |
| [, 3]	| disp | Displacement (cu.in.) |
| [, 4]	| hp | Gross horsepower |
| [, 5]	| drat | Rear axle ratio |
| [, 6]	| wt | Weight (lb/1000) |
| [, 7]	| qsec | 1/4 mile time |
| [, 8]	| vs | V/S |
| [, 9]	| am | Transmission (0 = automatic, 1 = manual) |
| [,10]	| gear | Number of forward gears |
| [,11]	| carb | Number of carburetors |


---


## Analysis - Main Code


```{r}
formulaText <- reactive({
    paste("carsData ~", input$variable)
  })
  
  formulaTextPoint <- reactive({
    paste("carsData ~", "as.integer(", input$variable, ")")
  })
  
  fit <- reactive({
    lm(as.formula(formulaTextPoint()), data = carsData)
  })

  output$caption <- renderText({
    formulaText()
  })

  output$modelBoxPlot <- renderPlot({
    boxplot(as.formula(formulaText()), 
            data = carsData,
            outline = input$variable)
  })
  
  output$fit <- renderPrint({
    summary(fit())
  })
  
  
  output$modelPlot <- renderPlot({
    with(carsData, {
      plot(as.formula(formulaTextPoint()))
      abline(fit(), col=2)
    })
  })
  output$explain <- renderText({
    "This peer assessed assignment has two parts.
     First, you will create a Shiny application and deploy it on Rstudio's servers.
     Second, you will use Slidify or Rstudio Presenter 
     to prepare a reproducible pitch presentation about your application. "
    })
```